%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Devops} % Role
    {Apex \tiny{\href{https://www.github.com/DarkGeekMS/ApeX-Server}{Back-end}~~~·~~~\href{http://www.github.com/DarkGeekMS/ApeX-Web}{Front-end}~~~·~~~\href{http://www.github.com/DarkGeekMS/ApeX-Mobile}{Android}~~~·~~~\href{https://www.github.com/DarkGeekMS/apeXTesting}{Test}}} % Event
    {} % Location
    {Jan-Mar 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Social Media app for web and android that mimics reddit.}
        \item {Worked with \textbf{18-member team}.}
        \item {Used ​ Travis-CI ​for CI/CD, \textbf{​GoogleCloud​}, Docker, \textbf{​DockerCompose​} and Datadog for monitoring.}
      \end{cvitems}
    }

  \cventry
    {Back-end Developer} % Role
    {Koos \tiny{\href{https://gitlab.com/koos-project/koos}{Repo}~~~·~~~\href{https://gitlab.com/koos-project/koos/tree/rust-migration/server}{Rust rewrite}}} % Event
    {} % Location
    {Jun 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Decentralised social media app, built on ​ \href{http://fluence.dev/}{Fluence​}, server is AssemblyScript/Rust, frontend is React.}
        \item {The project \href{https://www.linkedin.com/feed/update/urn:li:activity:6575339127934341120/}{​won​} a ​\href{https://gitcoin.co/issue/fluencelabs/Bounties/1/3290}{Gitcoin bounty​} from fluence for the best app that uses the technology.}
      \end{cvitems}
    }

  \cventry
    {Developed Solving code, ~Tester} % Role
    {TheMistake \tiny{\href{https://www.github.com/Abdulrahman-Khalid/mazeSolver}{Repo}}} % Event
    {} % Location
    {Jan-Mar 2019} % Date(s)
    {
      {Maze Solver ​ car using flood fill algorithm on \href{http://www.ti.com/tool/EK-TM4C123GXL}{​TIVA-C ​μc}​/Arduino Uno with ultrasonic and IR sensors.}
    }

  \cventry
    {Developed GUI and stickers drawing, ~Implemented HOG} % Role
    {Cartoonization \tiny{\href{http://github.com/Abdulrahman-Khalid/Cartoonization/}{Repo}}} % Event
    {} % Location
    {Oct-Dec 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Draw colorful stickers on your selfie face.}
        \item {Snapchat Clone written in Python.}
        \item {Using ​Viola-jones/Hog ​to detect faces, and multiple \textbf{image processing} techniques to filter the input.}
      \end{cvitems}
    }

  \cventry
    {Developer} % Role
    {RetroSoccer \tiny{\href{https://github.com/mido3ds/retrosoccer}{Repo}}} % Event
    {} % Location
    {Jan-Mar 2019} % Date(s)
    {
      {\textbf{Multiplayer​} football ​game​ entirely in x86 IA32 MASM \textbf{​assembly​} with chat (serial communication).}
    }

  \cventry
    {Developer} % Role
    {JetSimulator \tiny{\href{https://github.com/mido3ds/JetSimulator}{Repo}}} % Event
    {} % Location
    {Oct-Dec 2018} % Date(s)
    {
      {C++ 3D​ ​flight simulator​ using Opengl, started as graphics school project.}
    }

  \cventry
    {Developer} % Role
    {Paint-For-Kids \tiny{\href{https://github.com/mido3ds/paint-for-kids}{Repo}}} % Event
    {} % Location
    {Jan-Mar 2017} % Date(s)
    {
      {C++ ​GUI​ application for kids to ​ draw​ and play with shapes, with ​two game-modes​, OOP school project.}
    }

  \cventry
    {Developer} % Role
    {Outbreak \tiny{\href{https://github.com/mido3ds/Outbreak}{Repo}}} % Event
    {} % Location
    {Jun 2018} % Date(s)
    {
      {Java​/libgdx re-implementation of the classic ​game​ ``Outbreak”.}
    }

  \cventry
    {Developer} % Role
    {InventoryApp \tiny{\href{https://github.com/mido3ds/InventoryApp}{Repo}}} % Event
    {} % Location
    {Jun 2018} % Date(s)
    {
      Android​ app to keep track of inventory ​items of a store​.
    }

  \cventry
    {Developer} % Role
    {NesEmu \tiny{\href{https://github.com/mido3ds/nesemu}{Repo}}} % Event
    {} % Location
    {Ongoing} % Date(s)
    {
      NES console ​emulator​ in C++.
    }

  \cventry
    {Tester} % Role
    {Simple PDP--11 \tiny{\href{https://github.com/mido3ds/simple-pdp11}{Repo}}} % Event
    {} % Location
    {Oct-Dec 2019} % Date(s)
    {
      Design and simulation of a CPU architecture similar to \emph{PDP--11} in VHDL and Vunit for testbenches.
    }

  \cventry
    {Developer} % Role
    {QuickNet \tiny{\href{https://github.com/mido3ds/QuickNet}{Repo}}} % Event
    {} % Location
    {Ongoing} % Date(s)
    {
      C++11 web framework​ written from scratch, using sockets, no dependencies.
    }

\end{cventries}


